---
title: "2021 Hockey Non-Parametric"
author: "Nicholas Jacob"
date: "3/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
data = read.csv('https://raw.githubusercontent.com/nurfnick/RTest/main/hockey.csv')
```


This is a continuation of this project <https://rpubs.com/nurfnick/720194>

# Ranks

Most of these methods use ranks!  Let's go ahead and show the ranks!

```{r cars}
rank(data$PTS, ties.method = "average")
```

Some things to notice:

1. **R** automatically did the average, the option **ties.method** is not required but can be changed.
2.  The last score here is an **NA** BUT it returned as the highest ranked!  We'll need to fix that!

```{r}
rank(data$PTS, na.last = F)
```

I put the **NA** as the first (or lowest rank).  Notice though it does change all the ranks!

# Wilcox Rank Sum

## Fixed Value
Let me do a test against a value first.  I am going to ask is the median number of games played 4.

What was the median?
```{r}
median(data$GP, na.rm = TRUE)
```
Okay well this will at least be an interesting test then!

```{r}
wilcox.test(data$GP, mu = 4, na.rm = TRUE)
```
I do reject the null hypothesis!
```{r}
ggplot(data, aes(GP))+
  geom_boxplot()
```

## Compare Two Medians

I'll examine the variable describing if you are staying out of the penalty box or not

This code has been used before.
```{r}
data$PTS[is.na(data$PTS)] <- 0
data$PPO[is.na(data$PPO)] <- 0
data$PPOA[is.na(data$PPOA)] <- 0
data[which(data$PPO <= data$PPOA),"PowerPlays"] = "Less"
data[which(data$PPO > data$PPOA),"PowerPlays"] = "More"
```

I went ahead and assigned the team with no games zero points too.


Let's summarize the data we'll be comparing before we run the test
```{r}
by(data$PTS,data$PowerPlays, median)
```

```{r}
table(data$PowerPlays)
```

Let's run the test!
```{r}
wilcox.test(PTS ~ PowerPlays, data = data)
```

We will fail to reject the null hypothesis.  Take as many penalties as you want!  This was the previous result too!

# Wilcox Sign Test

I need matched data!  I am actually going to look at the same idea PowerPlay Attempts vs Your Opponents but rather than set up a categorical variable, I'll compare those two values.  My assumption is that if you are a mean team, taking lots of penalties, your opponent will too.

This is different from above!  I could subtract the two columns or just add that they are paired.  I'll show that both are the same


```{r}
wilcox.test(data$PPO, data$PPOA, paired = TRUE)
```
```{r}
wilcox.test(data$PPO - data$PPOA)
```
Easy enough!  We fail to reject the null hypothesis, there is not evidence to suggest that the number of powerplay opportunities and opponent opportunities are the same.

# Kruskal-Wallis

Just like the ANOVA, we need more than two categories to compare
```{r}
data$PPO[is.na(data$PPO)] <- 0
data$PPOA[is.na(data$PPOA)] <- 0
data[which(data$PPO < data$PPOA),"PowerPlays"] = "Less"
data[which(data$PPO > data$PPOA),"PowerPlays"] = "More"
data[which(data$PPO == data$PPOA),"PowerPlays"] = "Equal"
```

Looking at the median and seeing if the **PTS** stay the same

```{r}
model = kruskal.test(PTS ~ PowerPlays, data = data)
model
```
```{r}
ggplot(data, aes(PTS,PowerPlays))+
  geom_boxplot()
```
```{r}
table(data$PowerPlays)
```

We do not have evidence to suggest that the number of points depends on having more or less powerplays.  We fail to reject the null hypothesis.

# Spearman Rank Correlation

I'll again look at Wins and Points.

```{r}
cor.test(data$W,data$PTS, method = "spearman")
```
```{r}
ggplot(data,aes(W,PTS))+
  geom_jitter()
```

There is a strong correlation!  We'll reject the null hypothesis that the spearman correlation is zero but we do not know if we have a linear relationship.