---
title: "2021 Hockey Contingency Tables"
author: "Nicholas Jacob"
date: "2/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data = read.csv('https://raw.githubusercontent.com/nurfnick/RTest/main/hockey.csv')

```

# Contingency Tables and Tests For Independance
```{r}
data
```
This is a continuation of this project <<https://rpubs.com/nurfnick/720194>

This portion of the project is all about categorical variables.  Let's remind ourselves of what categorical variables we have.  I had created one about who had more powerplays, so I'll copy/pasta that code here
```{r}
data$PPO[is.na(data$PPO)] <- 0
data$PPOA[is.na(data$PPOA)] <- 0
data[which(data$PPO <= data$PPOA),"PowerPlays"] = "Less"
data[which(data$PPO > data$PPOA),"PowerPlays"] = "More"
```

```{r}
table(data$PowerPlays)
```
Let's add an indicator for Canadian teams too
```{r}
data[which(data$X %in% c("Toronto Maple Leafs","Montreal Canadiens","Calgary Flames","Winnipeg Jets" ,"Ottawa Senators","Edmonton Oilers")),"Canadian"] = TRUE
data[which(!(data$X %in% c("Toronto Maple Leafs","Montreal Canadiens","Calgary Flames","Winnipeg Jets" ,"Ottawa Senators","Edmonton Oilers"))),"Canadian"] = FALSE
table(data$PowerPlays,data$Canadian)
```


## Test For Independance



```{r}
test = chisq.test(table(data$PowerPlays), p = c(1,1)/2)
test
```
```{r}
test$expected
```

```{r}
barplot(table(data$PowerPlays))
```

## Contingency Table Test

```{r}
test2 = chisq.test(table(data$PowerPlays,data$Canadian))
test2
```

```{r}
test2$expected
```

```{r}
mosaicplot(table(data$PowerPlays,data$Canadian))
```




I am so clever























