---
title: "2021 Hockey"
author: "Nicholas Jacob"
date: "1/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data = read.csv('https://raw.githubusercontent.com/nurfnick/RTest/main/hockey.csv')
```

## Hockey Rules

I am testing

```{r}
head(data)
```

## Creating Project Part 0

1. Exploratory Data Analysis of Quantitative
2. Exploratory of One Categorical
3. Exploratory of Two Categorical
4. Hypothesis Test Comparing Mean to a Fixed Value
5. Hypothesis Test Comparing Two Means

```{r histogram}
hist(data$PTS)
```

```{r}
summary(data$PTS)
```

```{r}
sd(data$PTS, na.rm = TRUE)
```

```{r}
qqnorm(data$PTS)
```

```{r}
boxplot(data$PTS)
```

## Categorical Variables

```{r}
table(data$X)/length(data$X)
```

```{r}
table(data$X,data$GP)
```

## Hypothesis Test

$$
H_0:  \mu = 3\\
H_A:  \mu\neq 3
$$

```{r}
t.test(data$GP, mu = 3.25)
```
```{r}
lesspp = data[which(data$PPO <= data$PPOA),]
morepp = data[which(data$PPO > data$PPOA),]
```

```{r}
t.test(lesspp$W,morepp$W)
```




```{r}
t.test(data$GP, mu = 4)
```

The entire project can be found at the following links.  Note the number corresponds to the part of the project.


0. Hypothesis Testing <https://rpubs.com/nurfnick/715604>
1. Regression <https://rpubs.com/nurfnick/720194>
2. Bootstrapping and Cross Validation<https://rpubs.com/nurfnick/751598>
3. Contingency Tables and Goodness of Fit <https://rpubs.com/nurfnick/730831>
4. ANOVA <https://rpubs.com/nurfnick/733670>
5. NonParametric <https://rpubs.com/nurfnick/743967>